Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-09-01 reanalysis-5-outcome_analysis.qmd
final
correct ses

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "test"  # Should match imputation mode

@@

```{r fit-models}
# Check if models are already cached
models_cache_file <- file.path(reanalysis_data_dir, "fitted_models_main_effects.rds")
force_refit <- TRUE  # Set to TRUE if you want to force re-fitting

if (file.exists(models_cache_file) && !force_refit) {
  # Load cached models
  cached_models <- readRDS(models_cache_file)
  fitted_models <- cached_models$fitted_models
  model_summaries <- cached_models$model_summaries
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE

@@

```{r marginal-effects}
# Check if marginal means are cached
emmeans_cache_file <- file.path(reanalysis_data_dir, "emmeans_results_main_effects.rds")
force_recalc_emmeans <- TRUE  # Set to TRUE to force recalculation

>>>>

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "final"  # Should match imputation mode

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- FALSE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- TRUE  # Set to TRUE to recalculate marginal means

@@

```{r fit-models}
# Check if models are already cached
models_cache_file <- file.path(reanalysis_data_dir, "fitted_models_main_effects.rds")

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models
  cached_models <- readRDS(models_cache_file)
  fitted_models <- cached_models$fitted_models
  model_summaries <- cached_models$model_summaries
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE

@@

```{r marginal-effects}
# Check if marginal means are cached
emmeans_cache_file <- file.path(reanalysis_data_dir, "emmeans_results_main_effects.rds")
